---
title: "Final Project"
subtitle: "linear regression on insurance data"
author: "Leon Yuan"
date: "`r Sys.Date()`"
abstract: "This is a linear regression model."
thanks: "Hunter, Dr. McGee, Leon"
format: pdf
editor: visual
---

Our goal is to predict the charges based on the given predictors.

# Import data

```{r}
#| output: false
library(tidyverse)
```

```{r}
insurance <- read_csv("./data/insurance.csv")
View(insurance)
```

# EDA

## Check missing

This data is complete and no missing data.

```{r}
library(Amelia)
missmap(insurance, main = "Missing values vs observed")
```

## charges

```{r}
boxplot(charges ~ sex, data = insurance)
```

## ages

```{r}
boxplot(age ~ sex, data = insurance)
```

## how many each gender

```{r}
insurance %>%
  count(sex) %>%
  ggplot(aes(x=sex, y=n, fill = sex)) +
  geom_bar(stat = "identity", width = 0.5) +
  scale_fill_manual(values=c("#354CA1", "#CC0035")) +
  labs(title = "Sex Count") +
  theme_light() +
  theme(
plot.title = element_text(color="#354CA1", size=25, face="bold.italic", hjust = 0.5),
axis.title.x = element_text(color="#CC0035", size=20, face="bold"),
axis.title.y = element_text(color="#CC0035", size=20, face="bold"),
axis.text.x = element_text(size=15),
axis.text.y = element_text(size=15),
legend.title = element_text(size = 18),
legend.text = element_text(size = 15)
)
ggsave(filename = "sex count.pdf", path = "./img")
```

## bmi

```{r}
boxplot(bmi ~ sex, data = insurance)
```

## children

```{r}
boxplot(children ~ sex, data = insurance)
```

## smoker

```{r}
insurance %>%
  count(smoker) %>%
  ggplot(aes(x=smoker, y=n, fill = smoker)) +
  geom_bar(stat = "identity", width = 0.5) +
  scale_fill_manual(values=c("#354CA1", "#CC0035")) +
  labs(title = "Smoker Count") +
  theme_light() +
  theme(
plot.title = element_text(color="#354CA1", size=25, face="bold.italic", hjust = 0.5),
axis.title.x = element_text(color="#CC0035", size=20, face="bold"),
axis.title.y = element_text(color="#CC0035", size=20, face="bold"),
axis.text.x = element_text(size=15),
axis.text.y = element_text(size=15),
legend.title = element_text(size = 18),
legend.text = element_text(size = 15)
)
ggsave(filename = "smoker count.pdf", path = "./img")
```

## region

```{r}
insurance %>%
  count(sex, region)
```

# Simple or Oridinary linear regression

## First of all, convert categorical variables into factor or dummy variables

```{r}
insurance$sex <- factor(insurance$sex, levels = c("male", "female"), labels = c("male", "female"))
insurance$smoker <- factor(insurance$smoker, levels = c("yes", "no"), labels = c("yes", "no"))
insurance$region <- factor(insurance$region)
```

## Check factor variables

```{r}
# sex
contrasts(insurance$sex)
```

```{r}
# smoker
contrasts(insurance$smoker)
```

```{r}
# region
contrasts(insurance$region)
```

## simple linear regression without any processing

```{r}
lm.fit <- lm(data = insurance, charges ~ .)
```

```{r}
summary(lm.fit)
```

## diagnotical analysis

It's bad.

```{r}
plot(lm.fit)
```

## transform the `bmi` into 1/bmi

```{r}
insurance_bmi <- insurance
insurance_bmi$bmi <- 1/insurance_bmi$bmi
View(insurance_bmi)
```

```{r}
lm.fit.bmi <- lm(data = insurance_bmi, charges ~ .)
summary(lm.fit.bmi)
```

## Create the interaction between bmi and age

```{r}
lm.fit.bmi_age <- lm(data = insurance, charges ~ . + bmi * age)
summary(lm.fit.bmi_age)
```

# Random Forest model

```{r}
library(randomForest)
library(caret)
```

```{r}
rf <- randomForest(charges ~ ., data=insurance, proximity=TRUE)
print(rf)
```

```{r}
## Look at variable importance:
round(importance(rf), 2)
```
